
\section{Interfaces with existing solutions}

We envision Lakat as a base layer for an open, pluralistic and collaborative publication system that progresses through continuous integration. As a base layer we strive to rely only on a bare minimum of other software and aim to have interface with for existing software or protocols. Here we provide an overview of the protocols and software that we plan to build upon. 

We would like to interface with mediawiki. Mediawiki is an evolving database schema with a php frontend that allows for the creation of knowledge databases such as wikipedia. There are various
ways how Lakat could interface with mediawiki. The weakest form requires the conversion of the data contributions in Lakat to database entries in mediawiki. A stronger form converts also contributions to mediawiki into Lakat contributions. Regarding storage we aim to stay agnostic and leave the storage protocol as a configurable option. As options we consider IPFS, Ceramic (which is built on top of IPFS and anchored in Ethereum) and Urbit (lineDB).Regarding the token layer we aim to be agnostic here as well. Since this is an optional feature it is left to the branch contributors to decide and merge updates on their token transactions into their branch. We do recomment to deploy tokens on Polygon though and plan to integrate this into the pipeline.

Finally, regarding version control we would like to reduce the complexity of branch operations to a bare minimum in order to avoid security threats and reliance on other protocols. For the local consensus mechanism we believe that a heavily reduced set of operations is favourable. Nevertheless we would like to interface with existing version control systems such as git or radicle. We would like to interface with git or radicle in order to allow for the conversion of git or radicle repositories into Lakat branches. 



% We consider the following options: Ethereum, Urbit, Holochain, IOTA, Avalanche, Cardano, Polkadot, Cosmos, Solana, Algorand, Tezos, NEM, EOS, Tron, NEO, Stellar, Waves, Hedera, Zilliqa, Qtum, ICON, Lisk, Nano, BitShares, Komodo, Verge, Bytecoin, Siacoin, Steem, Stratis, Ardor, PIVX, Ark, Decred, MaidSafeCoin, Aeternity, Nxt, Metaverse ETP, Horizen, HyperCash, ReddCoin, MonaCoin, Syscoin, Nexus, Enjin Coin, Nebulas, Particl, NavCoin, Groestlcoin, NULS, RChain, GXChain, Nxt, Metaverse ETP, Horizen, HyperCash, ReddCoin, MonaCoin, Syscoin, Nexus, Enjin Coin, Nebulas, Particl, NavCoin, Groestlcoin, NULS, RChain, GXChain, Factom, Zcoin, Veritaseum, Aion, Ark, Komodo, Verge, Bytecoin, Siacoin, Steem, Stratis, Ardor, PIVX, MaidSafeCoin, Aeternity, Nxt, Metaverse ETP, Horizen, HyperCash, ReddCoin, MonaCoin, Syscoin, Nexus, Enjin Coin, Nebulas, Particl, NavCoin, Groestlcoin, NULS, RChain, GXChain, Factom, Zcoin, Veritaseum, Aion, Ark, Komodo, Verge, Bytecoin, Siacoin, Steem, Stratis, Ardor, PIVX, MaidSafeCoin, Aeternity, Nxt, Metaverse ETP, Horizen, HyperCash, ReddCoin, MonaCoin, Syscoin, Nexus, Enjin Coin, Nebulas, Particl, NavCoin, Groestlcoin, NULS, RChain, GXChain, Factom, Zcoin, Veritaseum, Aion, Ark, Komodo, Verge, Bytecoin, Siacoin, Steem, Stratis, Ardor, PIVX, MaidSafeCoin, Aeternity, Nxt, Metaverse ETP, Horizen

