
\section{Onramping}

One of the objectives of Lakat is to transition academic publishing from a paper-formatted system to a cryptographically secure, collaborative and pluralistic system that allows for the continuous integration of research output. In order to achieve this objective, we believe that a transition should be as seemless as possible. The publishing system with isolated paper-formatted publications and intransparent review processes is an edge case of Lakat, an unsustainable and hacky one yet sufficient for onramping. We describe in which sense this is the case and how a transition could be achieved.

We can imagine a scenario for Lakat with a set of isolated branches. Each branch is controlled by a single legal entity, namely an academic journal. The academic journal is the content contributor, the storage contributor and the token contributor all in one. When a hypothetical researcher, say Alice (AI or human), wants to publish a paper, she has to send it to the journal. The branch that the journal  controls is simply the indexed collection of articles that have been submitted, respectively chained together cryptographically. For a journal to transition its content to such a branch state is anywhere between immediate -- by pointing the head of the branch to the storage locations of all content -- or a matter of running a script that creates a submit for each accepted article retrospectively.  Each paper is stored on a journal-controlled server, thus making the journal the sole storage provider. By adding the submissoin to the journal branch, the journal becomse the sole content contributor and retains all the rights of the contribution. The contribution is no longer owned by Alice at all. In this hypothetical oligarchic abberation of Lakat, a contribution is a submit with a single data bucket containing the paper. In summary, there is a way to map the classical publishing system into Lakat. Depending on the openness and licensing it might be difficult to either access or modify the content, but at least there is an entry point for the conversion.
Why is this unsustainable?  Given the design of Lakat, this branch would quite naturally undergo diversification through forking. At some point a researcher may create a branch routed in that journal branch, which is but a click. Maybe the incentive structure provided by the journal is soo strong that authors are willing to transfer all the rights to the journal voluntarily, but given Lakat's inherent ease of branching it will be a matter of time until there a diversification is to be expected.